Twisted 11-dimensional supergravity, I

### 2021-08-06 draft.tex
blah blah blah

Recall that such deformations are governed by the classical master equation: the parameterized family of actions $I + \alpha J$ is sensible only if 
\deq{
  \{I+ \alpha J, I + \alpha J \} = 0.
}
Since this must hold for all $\alpha$, and since the undeformed action $I$ is already a solution to the classical master equation, this reduces to the two conditions 
\deq[eq:2cond]{
  \{I,J\} = \{J,J\} = 0.
}
\begin{thm}
  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, I_\infty)$ on $X \times L$ constructed above. The local functional 
  \deq{
    J = \gamma (\del \gamma)^k,
  }
  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,I_\infty)$ as a $\Z/2\Z$-graded BV theory.
\end{thm}
\begin{proof}
  First off, we consider grading issues. In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$. The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$. As such, we have
  \deq{
    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
  }
  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.

>>>>

Recall that such deformations are governed by the classical master equation: the parameterized family of actions $S + g J$ is sensible only if 
\deq{
  \{S + g J, S + g J \} = 0.
}
Since this must hold for all $g$, and since the undeformed action $S$ is already a solution to the classical master equation, this reduces to the two conditions 
\deq[eq:2cond]{
  \{S,J\} = \{J,J\} = 0.
}
\begin{thm}
  Let $X$ be a Calabi--Yau manifold of complex dimension $2k+1$ and $L$ a smooth manifold of real dimension $2\ell + 1$, and consider the BV theory $(\cE, S_\infty)$ on $X \times L$ constructed above. The local functional 
  \deq{
    J = \gamma (\del \gamma)^k,
  }
  where $\gamma \in \Omega^1(X;L)$, defines a deformation of~$(\cE,S_\infty)$ as a $\Z/2\Z$-graded BV theory.
\end{thm}
\begin{proof}
  First off, we consider grading issues. In the $\Z$-grading on the free theory, the component $\gamma^{1,i;j}$ sits in degree $-2k-2\ell -2+i+j$. The local functional $J$ includes terms that are degree-$(k+1)$ polynomials in the components of $\gamma$, for which $\sum i = 2k+1$ and $\sum j = 2\ell + 1$. As such, we have
  \deq{
    \deg(J) =-  (2k+ 2\ell+ 2)(k+1) + 2k+2\ell + 2 = - k(2k+2\ell+2).
  }
  Thus $J$ defines an even local functional; of course, it does not define a local functional of degree zero.
